\documentclass[notitlepage,a4paper,12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{tabto}
\usepackage[yyyymmdd]{datetime}
\renewcommand{\dateseparator}{--}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}

% For clickable TOC
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	citecolor=black,
	filecolor=black,
	linkcolor=black,
	urlcolor=black
}

% For definitions
%\newtheorem{defn}{Definition}[section]
%\newtheorem{thrm}{Theorem}[section]
%\newtheorem{ex}[Example}[section]
\newtheorem*{ex}{Example}
\newtheorem*{defn}{Definition}
\newtheorem*{thrm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{result}{Result}


% For circled text
\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=0.8pt] (char) {#1};}}

% For equation system alignment
\usepackage{systeme,mathtools}
% Usage:
%	\[
%	\sysdelim.\}\systeme{
%	3z +y = 10,
%	x + y +  z = 6,
%	3y - z = 13}

\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
%If you want to title your bold things something different just make another thing exactly like this but replace "problem" with the name of the thing you want, like theorem or lemma or whatever
 
%used for matrix vertical line
\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother 
 
% Change chapter numbering
\newcommand{\mychapter}[2]{
	\setcounter{chapter}{#1}
	\setcounter{section}{0}
	\chapter*{#2}
	\addcontentsline{toc}{chapter}{#2}
}

\usepackage{fancyhdr,afterpage}
\pagestyle{fancy}
\fancyhf{}
\cfoot{\thepage}
\author{Bryan Greener \and Paul Phillips}
\title{Business Ethics:\\A Case Study on Ethics in the Workplace}


\begin{document}
\maketitle
\thispagestyle{empty}
\clearpage
\setcounter{page}{1}
%\tableofcontents{}
%\mychapter{1}{2018-01-11}
\section*{Introduction}
\paragraph{}More often now days the topic of ethics in business comes up. With the global connectivity that the internet provides it is easier than ever to raise awareness of a company's wrongdoings. Thus the topic of ethics in business has grown larger than ever and must be dissected in order to better understand how businesses should conduct themselves.

\paragraph{}This study will cover the generalized idea of ethics, ethical standards in business specifically relating to computer science, laws that impact how a business is allowed to operate, and the policies that companies set for themselves and how they reflect the business' ethical image.

\paragraph{}The intent of this paper is not to tell the audience what constitutes a "proper" code of ethics but to educate in hopes that it allows them to form their own code of ethics and follow their own path.

\section*{Ethics}
\paragraph{}Merriam Webster defines ethics as being the discipline dealing with what is good and bad and with moral duty and obligation. This gives a very broad meaning to the word ethics, however and so the meaning of this word must be explored further. The two types of ethics that are important to this study are individual and business ethics. There is a strong connection between these two areas since the ethics that are shared between the majority of individuals are what generally determine the ethical code that a business follows. To understand this connection, it is important to understand the ethics of an individual.
\paragraph{}Every person has their own ethical code. This code is developed by the environments and encounters that a person experiences throughout their life. While there may be outliers here and there, for the most part a person will develop a set of ethics that matches that of their community. This is where business ethics come in to play. The community of individuals with similar ethics dictates how businesses conduct themselves. This is because a company needs to have a good public image in order to succeed. If a company doesn't follow the ethical code that is most prevalent in their target market then they must swim against the current and work harder to make sales. Clearly this is not a good business strategy as working harder typically requires more money. Thus there is a balance formed between the ethics of individuals and the ethical standards that companies follow.

\section*{Ethical Standards}
\paragraph{}In the world of programming and information technology there are two ethical standards that are indispensable: the Association for Computing Machinery (ACM) and the IEEE standards. Both groups are large communities that help form standards for how both individuals and businesses in computing should act in both the technical and the ethical sense. Though it is outside the scope of this study, it is important to know the more common standards set by IEEE, most notably the 802.x set of wireless standards which specify the formatting of LAN/MAN data packets and their transmission. These standards are necessary knowledge for anyone pursuing a career in programming and IT. However the focus of this paper is to dissect the ethical standards of each group, not the technical standards.
\paragraph{ACM Code of Ethics}The ACM code of ethics is split into four categories. We will examine each in depth to better understand how they tie in with each other. The fourth category is omitted from this review as it only specifies that a person or business will observe these standards and follow them otherwise they will not be able to consider themselves ACM compliant.
\paragraph{}The first section is "General Moral Imperatives" and contains very basic ethics that are mostly intuitive. This section includes topics such as avoiding harm to others, contributing to human well-being, being honest, and observing intellectual property laws. As an employee you will not usually run into issues with any of these as your work will be well defined ahead of time by the employer who should be managing the legal side of the project. Along with that, as long as the employer follows ethical standards when laying out a project then the employee shouldn't be in any position to infringe on basic human rights given they follow the guidelines laid out for them. The overall message that this section conveys is that both individuals and businesses should inconvenience others as little as possible as to keep everyone happy.
\paragraph{}The second section titled "more specific professional responsibilities" focuses more on the business environment and how professional workplaces should operate. Many of the points made focus on employees and employers producing the best product possible within reason and carrying out contracts properly. Following this section will help to avoid running into any legal conflicts but it will also make the individual or business look more professional which will in turn help to keep the customers coming.
\paragraph{}The third section, "organizational leadership imperatives", has a note mentioning that it draws from the IFIP code of ethics, namely the IFIP organizational ethics and international concerns sections. This section focuses entirely on how business owners and managers should operate their business in order to make their employees and their customers human rights in tact. For example, standard 3.2 in the ACM code of ethics is to "manage personnel and resources to design and build information systems that enhance the quality of working life." This particular standard is summarized as follows
	\begin{quote}
	Organizational leaders are responsible for ensuring that computer systems enhance, not degrade, the quality of working life. When implementing a computer system, organizations must consider the personal and professional development, physical safety, and human dignity of all workers. Appropriate human-computer ergonomic standards should be considered in system design and in the workplace.
	\end{quote}
To sum up, this standard's focus is to improve the happiness of personnel by providing good workplace conditions. An example of one of these improvements would be providing ergonomic mice and keyboards for employees. This is something that may seem very obvious however it is often such a small change that many people may overlook something like this when planning out a workplace. There are many examples of changes that would improve personnel happiness, many of which fall under OSHA compliance requirements, but this is a good example of one of the many fine details that must be looked into when following these ethical standards.
\paragraph{}Overall, many of the ethical standards observed by ACM may seem intuitive however it is easy for both individuals and businesses to overlook some of the finer details as often is the case. Thus having ACM publish these standards publicly helps people keep track of where they can improve both the well-being of the stakeholders of a company and its public image.
\paragraph{IEEE Code of Ethics}The IEEE code of ethics is a much shorter and more generalized list than the ACM code of ethics, though this does not make it any less important to observe. That said, many of the ACM and IEEE ethics overlap such as being honest, avoiding discrimination, avoiding harm to people, and so on. Thus we will focus on new concepts provided by the IEEE ethics. Each new concept is stated then examined in detail to better understand its effects.
	\begin{quote}
	Improve the understanding by individuals and society of the capabilities and societal implications of conventional and emerging technologies, including intelligent systems.
	\end{quote}
\paragraph{}This is the first new concept that we see in the IEEE standards. One of the biggest fears people have with technology is that it will end in a Terminator-esque rise of artificial intelligence. It is the job of people in technological fields to inform the public of how these new technologies will work as to avoid any fear of problems that may not even be in the realm of possibilities. That said, if there are actually some negative outcomes that could arise then the public must not be kept in the dark as it is not ethical to hide that information either. In the end, people do not like being uninformed so it is best to keep everyone up to date with emerging technologies.
	\begin{quote}
	Maintain and improve our technical competence and to undertake technological tasks for others only if qualified by training or experience, or after full disclosure of pertinent limitations.
	\end{quote}
\paragraph{}This concept can apply to any type of work however it is aimed toward technology in particular since this is the IEEE code. This is saying that a person should not take a job that they cannot complete without first informing the appropriate people of their inability to complete the task. This benefits both parties as it will not look good for the person that fails to complete the task and the customer would also be left without a promised product or service that was promised to them. Thus this standard should come as intuition but it is a firm reminder to a person to not over-promise when negotiating with clients.
\paragraph{}There are many more organizations and codes that lay out ethical standards for both individuals and for businesses however the ACM and IEEE codes of ethics gives a solid base that one can build on in order to develop a code of ethics for themselves or for their business. Though at the end of the day the client is the focus and so any ethical standards that are followed should appeal to the majority of clients in order to generate the largest reliable customer base.

\section*{Laws}
\paragraph{}There are many laws that come into play when operating a business or even developing products for distribution as an individual. However we will focus on laws that affect the moral and ethical decisions made when producing a technological product. These laws can be split into four major categories. This does not mean that more categories do not exist, these are simply the biggest categories that should be highest priority in the United States.
\paragraph{International}International laws clearly only apply when expanding outside of the United States however these laws should still be observed in order to prevent any issues further down the line when expanding the business. The most widely accepted laws are ones that maintain basic human rights. The basic human rights specified by the UN include the following rights that everyone is entitled to without any discrimination based on any aspect of a person or group of people:
	\begin{itemize}
	\item Everyone has the right to life, liberty, and security of person.
	\item No one shall be held in slavery or servitude.
	\item No one shall be subjected to torture or cruel, inhumane, or degrading treatment or punishment.
	\item Everyone has the right to recognition everywhere as a person before the law.
	\item All are equal before the law and are entitled without any discrimination to equal protection of the law.
	\end{itemize}
\paragraph{}These are only a few of the many human rights established by the UN. There are many more organizations that set human rights laws however the UN is more widely known. There are also international organizations whose focus it is to set international laws for businesses and technology. One important organization to note is the International Technology Law Association. They are a non-profit association that helps set information technology and intellectual property laws for international business operations.
\paragraph{Federal}Along with following international business laws, businesses must also abide by laws that span the entire US such as laws set by the department of labor, HIPAA, FERPA, and many others. In this case, we will focus on the three mentioned here.
\paragraph{}The laws set by the US Department of Labor are widely known since every business in the United States must follow their laws. The Department of Labor has many agencies however they are best known for their Occupational Safety and Health Administration agency or OSHA for short. OSHA regulates and oversees all aspects of businesses pertaining to employee safety. In order to run a business in the United States, a company must undergo regular OSHA compliance evaluations which test for occupational hazards such as exposed wiring, trip/slip hazards, asbestos, and many other factors that could potentially cause an injury. Other than OSHA, the Department of Labor requires that companies post information for employees that inform them of their rights as an employee of the company. These include information regarding minimum wage, medical leave, equal employment, workers with disabilities, and much more. These posters can be found on www.dol.gov where there is a wide variety of information about employees rights.
\paragraph{}The Health Insurance Portability and Accountability Act also known as HIPAA is a more specific set of laws that apply to medical facilities. HIPAA outlines the type of information that is considered private and what actions can and cannot be performed on that information. HIPAA is one of the main reasons why fax machines exist as well since most means of transmitting documents are not approved by HIPAA to be secure enough to transmit sensitive information. HIPAA laws are focused not on employees or employers but on customers and patients in order to maintain patient confidentiality. It maintains a very strict set of rules that if broken must be reported and must undergo an audit. An example of this is something as small as an employee talking about a patient when any other individual not approved is within earshot. HIPAA requires that if any employee notices this then it must be reported as a HIPAA violation. Because of these strict regulations, it is important for people in the IT and programming field to review all work done with a fine tooth comb to verify that there is no chance of information being intercepted whether it is intentional or not.
\paragraph{}The Family Educational Rights and Privacy Act also known as FERPA is very similar to HIPAA but it is aimed toward educational facilities and how student educational records may be viewed and transmitted. An example of rights that this provides students is the right to view their educational records and control the disclosure of these records. FERPA gives some peace of mind to students in the sense that their grades with personally identifiable information is not open to the public. It also states that students have the right to report any illicit activities within the school to FERPA in order for legal action to be taken without any recourse directed toward the reporting student.
\paragraph{State and Local}Just as with federal laws, state must observe any higher laws and local must follow state and anything higher as well. In the United States, states may set more specific laws that are not covered by federal laws given the laws do not directly conflict each other. For example, federal laws set requirements for taxes and employee rights but Michigan also set laws that prevent discrimination based on a person's sexual orientation or gender. This of course varies from state to state. Local laws take this concept a step further and can set laws that are not covered in state or federal law. An example of this would be a city setting another anti-discrimination law that prevents businesses from discriminating based on political views.
\paragraph{}Each of these categories can be thought of as being part of a cascading permissions structure where international laws are at the root of the tree. These laws all work together to dictate how businesses can operate with the end goal of creating a safe and friendly workplace for everybody. From there, companies can form an even more localized set of ethical policies that create what is known as an organizational culture. The idea of organizational culture will be covered in the next section.

\section*{Company Policies}
\paragraph{}Each company has a unique set of policies that they follow but many of the same policies are shared between most businesses. The most common policies are usually employee conduct, time off policies, Non-disclosure Agreements (NDA), and non-compete clauses. Each company executes these policies with minor differences so we will focus on the most common examples.
\paragraph{Employee Conduct}These policies supersede an employee's position in a company. This ensures that regardless of their position, each person is expected to uphold a certain standard in order to maintain equality among all employees. These policies typically outline topics such as appropriate workplace conversations, respect in the workplace, use of company equipment, use of company time, dress code, safety procedures, and many more. This set of rules helps to form an organizational culture as well. An organizational culture is the informal set of values and behaviors that employees exhibit. By setting a clear set of rules regarding employee behavior, a company can avoid legal issues brought about by discrimination and harassment caused by a bad organizational culture.
\paragraph{Time Off}This policy defines how a company awards time off, vacation, and sick days within the legal limits. A company must observe the federal, state, and local laws regarding time off, sick days, and vacation, but they may also allow more than what is required. Allowing more time off typically boosts morale and helps to improve public image of the company. Most companies handle time off by using an award system based on the amount of time that an employee has been with the company. For example, an employee may receive an additional 48 hours of time off that they are permitted in a fiscal year for each year that they stay with the company.
\paragraph{NDAs}Non-disclosure Agreements are rules that an employee agrees to that specify what company information is to be kept confidential. These are used in order to preserve intellectual property and to prevent employees from selling important information to outside resources as this can damage a company's earnings.
\paragraph{Non-Compete Clauses}A non-compete clause is an agreement made between the employee and their employer that specifies any work that an employee performs outside of company time. This doesn't always mean that an employee can't perform any work out of company time for other companies. It is usually used to prevent employees from working on the side for a company whose profits directly negatively impact their own company's profits.
\paragraph{}Each of these policies helps shape a company and each reflects the company's ethical standards. By setting a good set of policies, the company can improve their public appearance in order to get more customers. This also improves their employee base as more people will seek out jobs in a friendly environment as opposed to a restrictive one.

\section*{Conclusion}
\paragraph{}By taking the concepts laid out in this paper, one should have a good understanding of how ethics play into business operation and how those business operations affect individuals. These ethics are applied in business by following a set of standards put forth by organizations such as ACM and IEEE or even by forming a unique set of ethics. Though these ethics must abide by law on every level from local to international. After this, a company is free to form their own set of policies that dictate things such as time off awards, NDAs, non-compete clauses, and more operational policies. The company can also mandate how employees must carry themselves along with suggestions that form an organizational culture. These all give a good jumping off point for any company to form their own identity and flourish.

\end{document}