\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage{tabto} %add \notab command
\usepackage[nottoc]{tocbibind} %embedded bibliography
\usepackage{tabularx}
\usepackage{arydshln} % gives hdashline and cdashline
\newcommand*{\tempb}{\multicolumn{1}{:c}{}} % Used for block matrices
\usepackage{hyperref}


\newcolumntype{R}{>{\raggedright\arraybackslash\hspace{0pt}} X}
\newcolumntype{S}{>{\centering  \arraybackslash\hspace{0pt}} X}
\newcolumntype{T}{>{\raggedleft \arraybackslash\hspace{0pt}} X}

% HEADER
% BEGIN BLOCK------------------------------------------
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
\lhead{WRanglr for NHANES}
\rhead{Presentation Report}
\chead{Bryan Greener}
\cfoot{\thepage}
% END BLOCK============================================


% TITLE
% BEGIN BLOCK------------------------------------------
\title{\huge WRanglr for NHANES\\
	\LARGE Presentation Report}
\author{Bryan Greener}
\date{2018-04-17}
\begin{document}
\maketitle
% END BLOCK============================================

\TabPositions{4cm}
\begin{center}
\textbf{Presentation Information}\\
\begin{tabular}{rl}
Date & 2018-04-17\\
Place & WMU Parkview Campus\\
Title of Talk & WRanglr for NHANES\\
\end{tabular}
\end{center}

This group presented a project for Dr. McKean wherein they developed a web based resource for data set manipulation. This project was inspired by their client who needed some easier way to access statistics tools in order to work with large data sets without the requirement of knowledge of a statistical computing language.\\

This project was directed toward people who do not necessarily know how to program any any languages but do know how to work with data sets. These people need something that sets up the data for them, has easy to use functions that are intuitive to non-programmers, and allows data set manipulation.\\

This group developed their project with the goal of making an easily maintainable solution that Dr. McKean could maintain on his own. With this goal in mind, they used Amazon cloud servers. This solution is known to be very secure and reliable. Also since Dr. McKean can program in R, he has a good background to maintain this project.\\

The introduction to this project was well paced and described in detail who their client was, what the need was, and any prospect ideas that they had to fill their client's needs. They covered the different aspects of the problem that helped them decide on using a web based R solution.\\

During the presentation, this group talked in detail about the reasoning behind any decisions made and any additional solutions that they considered but ended up not choosing as well as their reasons for not choosing that solution. The slides used during the presentation were somewhat bland as they only sometimes contained pictures related to the content of the slide. Other times I noticed that they covered too much information on one slide so they were talking for five minutes about the content on one slide. It made it hard to follow along visually with what they were talking about.\\

Each presenter had good volume and posture. They all seemed pretty confident and knowledgeable of the content that they were presenting. Again, the slideshow could have used some extra color and content to make it more informative. There was a definite difference in presenting skill between the presenters that made it seem like they didn't practice together as much as they should have. Also one of the presenters seemed to be deliberately talking slow during the first section of the presentation in order to meet the presentation time requirement.\\

There are a few things that I would do different from this group. First, I would make the slideshow a bit better by adding more graphics and changing the color scheme slightly. Another change that I'd make is I'd make sure everyone in the group is wearing matching sport jackets or suits. In one of the other presentations I went to the group all had matching attire and it made the presentation look very professional. Finally I would make sure that each group member is practiced enough to be confident while speaking and maintain the same speaking pace throughout the presentation. This helps to make the presentation look more professional and well rehearsed. 

\end{document}